Strings functions analysis

### 2022-08-28 article.tex
all js functions added

    \subsection{The table of functions in languages}

@@

            chop &  &  &  &  &  & &  &  &  & \\ \hline
        \end{tabular}
        \caption{String functions criteria}
        \label{tab:my_label}
    \end{table*}

    \subsection{String function metrics}

    \subsection{String functions of standard libraries}

@@

>>>>

@@

            chop &  &  &  &  &  & &  &  &  & \\ \hline
        \end{tabular}
        \caption{String functions existing in languages}
        \label{tab:my_label}
    \end{table*}

    \hl{todo String function metrics table}

    Below we have a list of all string functions from the standard libraries of the specified languages.

@@

    \textbf{JavaScript}: charAt, charCodeAt, codePointAt, concat, constructor, endsWith, fromCharCode, includes, indexOf, lastIndexOf, length, localeCompare, match, prototype, repeat, replace, search, slice, split, startsWith, substr, substring, toLocaleLowerCase, toLocaleUpperCase, toLowerCase, toString, toUpperCase, trim, valueOf.
